Placeholder

### 2021-02-20 Paper_Histograms.Rmd
Collapsed July to September sign ups together

>>>>

```{r Collapse July to September sign ups together}

dat.retro_july_sep_sign_up <- dat.retro_july_sign_up %>% 
  left_join(dat.retro_august_sign_up,
            by = "Sample_plot")

dat.retro_july_sep_sign_up <- dat.retro_july_sep_sign_up %>% 
  left_join(dat.retro_september_sign_up,
            by = "Sample_plot")

dat.retro_july_sep_sign_up %>% 
  group_by(Sample_plot) %>% 
  mutate("July-September" = 
           July + August + September) %>% 
  select(Sample_plot, "July-September")
